\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm Implementation

### 2024-12-13 paper/main.tex
small fix
paper: revise
paper: fix title

  notenote = {Accessed: 2024-11-12}

@@

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm}

@@

We would like to thank Brown's CS2680 and Professor Akshay Narayan for the help provided in the development of this project. The source code for all the artifacts (eBPF-Cubic, eBPFCCP, benchmark suite) is available at \url{https://github.com/claby2/ebpfcca}

>>>>

@@

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm Implementation}

@@

We would like to thank Brown's CS2680 and Professor Akshay Narayan for the help provided in the development of this project. The source code is available at: \\
\url{https://github.com/ebpfcca/ebpfcca}
